\documentclass{muratcan_cv}

\setname{Matin}{Hossein pour}
\setaddress{Birjand/Iran}
\setmobile{+989156676963}
\setmail{matin192hp@gmail.com}
\setposition{Work Student}
\setlinkedinaccount{https://www.linkedin.com/in/matin-hosseinpour}
\setgithubaccount{https://github.com/matinHosseinpour} 
\setthemecolor{red}

\begin{document}
%Set variables

%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}{
Hello, I am Matin, I am extremely interested in learning and learning will never end for me. I am very interested in JavaScript and Python and I love hard and challenging days. I'm very interested in programming and I enjoy working with JavaScript frameworks and I'm trying to master them all. I am very interested in academic research. In a word, I love computers and everything related to it.
}
%
%Education
\section{Education} 
    \datedexperience{Birjand University}{2018-2022 / Iran} 
    \explanation{B.S in Computer Engineering} 
     \explanationdetail{\coloredbullet\ % 
     Software Orientation
     }
     \explanationdetail{\coloredbullet\ % 
     Conducting research projects on the Internet of Things and artificial intelligence
     }
     \datedexperience{Birjand University}{2022-2024 / Iran} 
    \explanation{M.S in IT} 
     \explanationdetail{\coloredbullet\ % 
     IOT Researcher
     }
     \explanationdetail{\coloredbullet\ % 
     ML, Image Processing
     }
%
% Experience
\section{Experience}
    %
    \datedexperience{Pencode Inc.}{2018-2019 / Iran} 
    \explanation{Intern as front-end developer} 
    \explanationdetail{\coloredbullet\ 
    ‌Html - Css - Bootstrap - Javascript - Jquery - ES6
     }
    %
    \datedexperience{Noorab Inc.}{2019-2022 / Iran} 
    \explanation{Javascript Developer} 
    \explanationdetail{\coloredbullet\ 
    Development software for directing musical fountains using electronJS.
     }
     \explanationdetail{\coloredbullet\ 
    Use Raspberry Pi to send data to Musical Fountain using Python and serial communication.
     }
    %
    \datedexperience{Birjand University Information Technology Center}{2021-2023 / Iran} 
    \explanation{React Developer} 
    \explanationdetail{\coloredbullet\ 
    Redux - React Query - Material UI - Sass - Rest API - Typescript - React Router - Scrum
     }
    %
%
% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \  Python \cpshalf Javascript }}
    %
   \newcommand{\skillfive}{\createskill{}{\textbf{\emph{Familiar:}} \ \  Matlab \cpshalf C++ \cpshalf Latex \cpshalf Golang }}
    %
    \newcommand{\skilltwo}{\createskill{Research Fields}{Internet of things \cpshalf Data balancing in ML }}
    %
    \newcommand{\skillthree}{\createskill{Frameworks \ \& \ Libraries}{Jupyter \cpshalf Pandas \cpshalf Electronjs \cpshalf Reactjs \cpshalf Nodejs}}
    %
    \newcommand{\skillsix}{\createskill{}{Redux \cpshalf ReactQuery \cpshalf SQL \cpshalf Material-ui \cpshalf Bash scripting }}
    %
    \newcommand{\skillfour}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Persian \ \ \textbf{\emph{Fluent:}} \ \ English \ \ \textbf{\emph{Beginner:}} \ \  Arabic }}
    %
    \createskills{\skillone, \skillfive, \skilltwo, \skillthree, \skillsix, \skillfour}
%
% Experience
\section{Extra}
    \newcommand{\extraone}{%
    Member of the Central Council of Birjand University Computer Science Association
    }
    %
    \newcommand{\extratwo}{%
    Secretary of Birjand University Writers Association
    }
    %
    \newcommand{\extrathree}{%
    Editor of Arvand Magazine
    }
    \newcommand{\extrafour}{%
    Fluent in Linux
    }
    %
    \newcommand{\listofextras}{\extraone, \extratwo, \extrathree, \extrafour}
    %
    \createbullets{\listofextras}
%
%Footnote
\createfootnote
\end{document}
